\documentclass{article}
\usepackage{array}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.25in]{geometry}
\usepackage{multicol}
\setlength{\columnsep}{2cm}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{tgbonum}
\titleformat{\section}
{\huge\bfseries\camelcase}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\Large\bfseries\camelcase}
{\hspace{-.25in}}
{0em}
{}

\titleformat{\subsubsection}
{\bfseries}
{}
{0em}
{}

\titlespacing{\subsubsection}
{0em}
{.25em}
{.25em}


\renewcommand{\maketitle}{
    \begin{center}
    {\huge\bfseries
    \theauthor}
    \end{center}
}



\begin{document}
\fontfamily{phv}\selectfont


\title{Curriculum Vitae}
\author{Manuel Fl\"uckiger}

\maketitle
\section{Personal details}
\begin{itemize}[parsep = 0.05cm]
    \item[] Amselweg 5, 3427 Utzenstorf
    \item[] 076 576 17 49
    \item[]\href{mailto:manuel.flueckiger.mf@gmail.com}{manuel.flueckiger.mf@gmail.com}
    %\item[] \href{https://www.linkedin.com/in/manuel-fl%C3%BCckiger-43551b280/}{LinkedIn} 
\end{itemize}



\section{Technical Skills}
\begin{multicols}{2}
\subsection{Applications}
\subsubsection{Productivity}
\begin{tabular}{| m{5em} | m{12em} |}
    \hline
    \textbf{level} &  \textbf{Application} \\
    \hline
    good & Microsoft Word\\
    & Microsoft PowerPoint\\
    & Microsoft Excel\\
    \hline
    basic & Odoo\\
    \hline
\end{tabular}

\subsubsection{Creative}
\begin{tabular}{| m{5em} | m{12em} |}
    \hline
    \textbf{level} &  \textbf{Application} \\
    \hline
    good & Affinity Photo\\
    & Affinity Designer\\
    & Affinity Publisher\\
    & Adobe Photoshop\\
    & Pinnacle Studio\\
    \hline
    basic & Audacity\\
        & FFmpeg\\
    \hline
\end{tabular}
\subsection{Languages}

\subsubsection{Programming}
\begin{tabular}{| m{5em} | m{12em} |}
    \hline
    \textbf{level} &  \textbf{language} \\
    \hline
    advanced & Java \\
    \hline
    good & Python\\
    & JavaScript\\
    \hline
    basic &  C\\
    & ASM \\
    \hline
\end{tabular}
\subsubsection{Markup}
\begin{tabular}{| m{5em} | m{12em} |}
    \hline
    \textbf{level} &  \textbf{language} \\
    \hline
    good & HTML \\
    & CSS \\
    \hline
    basic &  LaTex \\
    \hline
\end{tabular}
\subsubsection{Query}
\begin{tabular}{| m{5em} | m{12em} |}
    \hline
    \textbf{level} &  \textbf{language} \\
    \hline
    advanced & MySQL\\
    & PostgreSQL\\
    \hline
\end{tabular}
\end{multicols}

\section{Job Experience}
\begin{itemize}[leftmargin=3cm, labelsep = 0.5cm ]
    \item[since 16.6.2023] \textbf{Full-Stack developer}\newline Theology Faculty of the University of Bern - Bern\newline
    Creating a webapplication to manage interviews conducted by the theological faculty of the University of Bern.
    Set up a VM on my private Server to host the project. Used Nodejs, Express, MySQL and Ngnix for the backend.
    Learned how to hash passwords, manage user sessions and handle requests to a webserver.
    \item[8.2022 - 3.2023] \textbf{Scanning employee, DMS Team}\newline FIVE Informatik AG - Sch\"onbühl \newline
    Assisting with the delivery of data, preparing documents for scanning, scanning with high performance scanners, 
    checking completeness, destruction and disposal of scanned data.
    \item[8.2010 - 6.2018] \textbf{Web-developer}\newline Eva J\"ackle - Kirchberg \newline 
    My Matura project. Learned HTML, CSS, MySQL and PHP. Rewrote the existing site into programmer friendly code,
    adapted it to work on mobile, and wrote the user interface for Ms. J\"ackle to edit the content of the page without
    having to edit HTML files.  \\
    \item[8.2010 - 6.2018] \textbf{Trial apprenticeship}\newline FIVE informatik AG - Sch\"onbühl \newline
    First experience with Python, HTML and PHP.\\ 
\end{itemize}

\section{Education}
\subsection{Academic Career}
\begin{itemize}[leftmargin=3cm, labelsep = 0.5cm ]
    \item[since 9.2022] \textbf{University of Bern} - BS in Computer Science \newline
    Minors: Mathematics, Information Systems, Psychology. Projected bachelor graduation in 2026.  \\
    \item[8.2018 - 6.2022] \textbf{Gymnasium of Burgdorf} - Major subject: Biology and Chemistry  \newline
     Subsidiary subjects: Computer Science, Matura thesis in Computer Science\\
    \item[8.2010 - 6.2018] \textbf{Elementary School Schule untere Emme} \newline
    2 years Secondary school I, 6 years primary school 
\end{itemize}
\subsection{Languages}
\begin{itemize}[leftmargin=3cm, labelsep = 0.5cm ]
    \item[Swissgerman]
    \begin{tabular}{| m{4em} | m{12em}}
        speaking& fluent (mother tongue)\\
        \hline
        writing  & error free\\
      \end{tabular}\newline
    \item[German]
    \begin{tabular}{| m{4em} | m{12em}}
        speaking & fluent\\
        \hline
        writing & proficient\\
    \end{tabular}
    \item[English]
    \begin{tabular}{| m{4em} | m{12em}}
        speaking & fluent\\
        \hline
        writing & proficient\\
    \end{tabular}
    \item[French]
    \begin{tabular}{| m{4em} | m{12em}}
        speaking & beginner to intermediate\\
        \hline
        writing & beginner\\
    \end{tabular}
    \item[Norwegian]
    \begin{tabular}{| m{4em} | m{12em}}
        speaking & beginner\\
        \hline
        writing & beginner\\
    \end{tabular}
\end{itemize}

\section{Hobbies}
\begin{itemize}
    \item I enjoy exploring technology in my free time, 
    including hosting virtual machines on my server (running ESXi), tinkering with Raspberry Pis, 
    and building computers for friends and family.
    \item I'm playing Volleyball in VBC Utzenstorf and at the University of Bern.
    \item I like to engage in language exchange with people from e.g. 
    Norway, Scotland, England, Turkey or Austria.
\end{itemize}

\section{Social Activities}
\begin{itemize}
    \item Spring camp assistant leader of the parish of Utzenstorf in the years of 2016/17/18
    \item Various assistant leader positions in parish activities such as bike tours or sledding
\end{itemize}
\end{document}